Testing Charts: viewers' perceptual accuracy in surveys

### 2023-07-31 SDSS-2023/testing-charts-accuracy.qmd
confidence intervals

```{r}
#| label: fig-demographics
#| fig-cap: "Response patterns by alignment and demographic levels. For aligned tiles, gender, age, and education are not significant factors. However, income levels do have a (small) effect. When income levels increase, the percentage of wrong answers decreases, while the percentage of correct answers increases slightly (significant at 5%). For the  more difficult task of comparing unaligned tiles, higher levels of education and higher levels of income are associated with a significant increase of panelists choosing a response of 'they are the same', resulting in significant decreases of both correct answers and wrong answers. "
#| fig-subcap: 
#|   - Comparisons of aligned tiles
#|   - Comparisons of unaligned tiles
#| fig-height: 4
#| fig-width: 10
#| layout-nrow: 2
#| out-width: 100%

educ_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = educ5)) + 
  facet_grid(~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby education") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)

educ_ab <- round_123_long %>% 
  filter(task=="ab") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = educ5)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby education") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)

gender_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = gender)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
  ggtitle("Accuracy\nby gender") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)

gender_ab <- round_123_long %>% 
  filter(task=="ab") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = gender)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
  ggtitle("Accuracy\nby gender") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)

income_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = income4)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="right",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby income") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)

income_ab <- round_123_long %>% 
  filter(task=="ab") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = income4)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="right",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby income") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)

age_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = age4)) + 
   facet_grid(.~task) + 
 geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby age") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)

age_ab <- round_123_long %>% 
  filter(task=="ab") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = age4)) + 
   facet_grid(.~task) + 
 geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby age") +
  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100)
gender_cd + age_cd  + educ_cd +income_cd + 
    plot_layout(nrow=1, guides = "collect", widths = c(2,4,5,4))

@@

>>>>

@@

```{r}
#| label: fig-demographics
#| fig-cap: "Response patterns by alignment and demographic levels. For aligned tiles, gender, age, and education are not significant factors. However, income levels do have a (small) effect. When income levels increase, the percentage of wrong answers decreases, while the percentage of correct answers increases slightly (significant at 5%). For the  more difficult task of comparing unaligned tiles, higher levels of education and higher levels of income are associated with a significant increase of panelists choosing a response of 'they are the same', resulting in significant decreases of both correct answers and wrong answers. "
#| fig-subcap: 
#|   - Comparisons of aligned tiles
#|   - Comparisons of unaligned tiles
#| fig-height: 4.5
#| fig-width: 10
#| layout-nrow: 2
#| out-width: 100%

educ_glm <- svyglm(correct~educ5-1, design=survey_123, family=quasibinomial(), subset = task=="cd")
educ_ci <- broom::tidy(educ_glm) %>%
  mutate(
    educ5 = factor(levels(round_123$educ5), levels = levels(round_123$educ5)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

educ_glm3 <- svyglm(correct3~educ5-1, design=survey_123, family=quasibinomial(), subset = task=="cd")

educ_ci3 <- broom::tidy(educ_glm3) %>%
  mutate(
    educ5 = factor(levels(round_123$educ5), levels = levels(round_123$educ5)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
educ_compare <- glht(educ_glm, mcp(educ5="Tukey"))
educ_compare3 <- glht(educ_glm3, mcp(educ5="Tukey"))

# get letters for each confidence
educ_ci$letters <- cld(educ_compare)$mcletters$Letters
educ_ci3$letters <- cld(educ_compare3)$mcletters$Letters

educ_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = educ5)) + 
  facet_grid(~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby education") +
    geom_segment(
    aes(
      x = as.numeric(educ5) - 0.45,
      y = estimate,
      xend = as.numeric(educ5) + 0.45,
      yend = estimate
    ),
    alpha = 1, colour = "black", linewidth = 0.25,
    data = educ_ci
  ) +
  geom_segment(
    aes(
      x = as.numeric(educ5) - 0.45,
      y = estimate,
      xend = as.numeric(educ5) + 0.45,
      yend = estimate
    ),
    alpha = 1, colour = "black", linewidth = 0.25,
    data = educ_ci3
  ) +
  geom_rect(
    aes(
      xmin = as.numeric(educ5) - 0.45,
      ymin = low,
      xmax = as.numeric(educ5) + 0.45,
      ymax = high,
    ),
    fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
    data = educ_ci
  ) +
  geom_rect(
    aes(
      xmin = as.numeric(educ5) - 0.45,
      ymin = low,
      xmax = as.numeric(educ5) + 0.45,
      ymax = high,
    ),
    fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
    data = educ_ci3
  ) +
  scale_y_continuous("Percentage", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25), limit=c(-.05, 1.05))  +
  geom_text(aes(label=letters), y = -0.05, data = educ_ci, colour = "steelblue") +
  geom_text(aes(label=letters), y = 1.05, data = educ_ci3, colour = "darkorange")

educ_glm <- svyglm(correct~educ5-1, design=survey_123, family=quasibinomial(), subset = task=="ab")
educ_ci <- broom::tidy(educ_glm) %>%
  mutate(
    educ5 = factor(levels(round_123$educ5), levels = levels(round_123$educ5)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

educ_glm3 <- svyglm(correct3~educ5-1, design=survey_123, family=quasibinomial(), subset = task=="ab")

educ_ci3 <- broom::tidy(educ_glm3) %>%
  mutate(
    educ5 = factor(levels(round_123$educ5), levels = levels(round_123$educ5)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
educ_compare <- glht(educ_glm, mcp(educ5="Tukey"))
educ_compare3 <- glht(educ_glm3, mcp(educ5="Tukey"))

# get letters for each confidence
educ_ci$letters <- cld(educ_compare)$mcletters$Letters
educ_ci3$letters <- cld(educ_compare3)$mcletters$Letters

educ_ab <- round_123_long %>% 
  filter(task=="ab") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = educ5)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby education") +
#  scale_y_continuous("Percentage", breaks=seq(0,1, by=0.25), labels = seq(0,1, by=0.25)*100) 
geom_segment(
  aes(
    x = as.numeric(educ5) - 0.45,
    y = estimate,
    xend = as.numeric(educ5) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = educ_ci
) +
geom_segment(
  aes(
    x = as.numeric(educ5) - 0.45,
    y = estimate,
    xend = as.numeric(educ5) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = educ_ci3
) +
geom_rect(
  aes(
    xmin = as.numeric(educ5) - 0.45,
    ymin = low,
    xmax = as.numeric(educ5) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = educ_ci
) +
geom_rect(
  aes(
    xmin = as.numeric(educ5) - 0.45,
    ymin = low,
    xmax = as.numeric(educ5) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = educ_ci3
) +
  scale_y_continuous("Percentage", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25), limit=c(-.05, 1.05))  +
 geom_text(aes(label=letters), y = -0.05, data = educ_ci, colour = "steelblue") +
 geom_text(aes(label=letters), y = 1.05, data = educ_ci3, colour = "darkorange")

########
# gender

gender_glm <- svyglm(correct~gender-1, design=survey_123, family=quasibinomial(), subset = task=="cd")
gender_ci <- broom::tidy(gender_glm) %>%
  mutate(
    gender = factor(levels(round_123$gender), levels = levels(round_123$gender)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

gender_glm3 <- svyglm(correct3~gender-1, design=survey_123, family=quasibinomial(), subset = task=="cd")

gender_ci3 <- broom::tidy(gender_glm3) %>%
  mutate(
    gender = factor(levels(round_123$gender), levels = levels(round_123$gender)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
gender_compare <- glht(gender_glm, mcp(gender="Tukey"))
gender_compare3 <- glht(gender_glm3, mcp(gender="Tukey"))

# get letters for each confidence
gender_ci$letters <- cld(gender_compare)$mcletters$Letters
gender_ci3$letters <- cld(gender_compare3)$mcletters$Letters

gender_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = gender)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
  ggtitle("Accuracy\nby gender") +
 geom_segment(
  aes(
    x = as.numeric(gender) - 0.45,
    y = estimate,
    xend = as.numeric(gender) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = gender_ci
) +
geom_segment(
  aes(
    x = as.numeric(gender) - 0.45,
    y = estimate,
    xend = as.numeric(gender) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = gender_ci3
) +
geom_rect(
  aes(
    xmin = as.numeric(gender) - 0.45,
    ymin = low,
    xmax = as.numeric(gender) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = gender_ci
) +
geom_rect(
  aes(
    xmin = as.numeric(gender) - 0.45,
    ymin = low,
    xmax = as.numeric(gender) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = gender_ci3
) +
  scale_y_continuous("Percentage", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25), limit=c(-.05, 1.05))  +
 geom_text(aes(label=letters), y = -0.05, data = gender_ci, colour = "steelblue") +
 geom_text(aes(label=letters), y = 1.05, data = gender_ci3, colour = "darkorange")

gender_glm <- svyglm(correct~gender-1, design=survey_123, family=quasibinomial(), subset = task=="ab")
gender_ci <- broom::tidy(gender_glm) %>%
  mutate(
    gender = factor(levels(round_123$gender), levels = levels(round_123$gender)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

gender_glm3 <- svyglm(correct3~gender-1, design=survey_123, family=quasibinomial(), subset = task=="ab")

gender_ci3 <- broom::tidy(gender_glm3) %>%
  mutate(
    gender = factor(levels(round_123$gender), levels = levels(round_123$gender)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
gender_compare <- glht(gender_glm, mcp(gender="Tukey"))
gender_compare3 <- glht(gender_glm3, mcp(gender="Tukey"))

# get letters for each confidence
gender_ci$letters <- cld(gender_compare)$mcletters$Letters
gender_ci3$letters <- cld(gender_compare3)$mcletters$Letters

gender_ab <- round_123_long %>% 
  filter(task=="ab") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = gender)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
  ggtitle("Accuracy\nby gender") +
   geom_segment(
  aes(
    x = as.numeric(gender) - 0.45,
    y = estimate,
    xend = as.numeric(gender) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = gender_ci
) +
geom_segment(
  aes(
    x = as.numeric(gender) - 0.45,
    y = estimate,
    xend = as.numeric(gender) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = gender_ci3
) +
geom_rect(
  aes(
    xmin = as.numeric(gender) - 0.45,
    ymin = low,
    xmax = as.numeric(gender) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = gender_ci
) +
geom_rect(
  aes(
    xmin = as.numeric(gender) - 0.45,
    ymin = low,
    xmax = as.numeric(gender) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = gender_ci3
) +
  scale_y_continuous("Percentage", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25), limit=c(-.05, 1.05))  +
 geom_text(aes(label=letters), y = -0.05, data = gender_ci, colour = "steelblue") +
 geom_text(aes(label=letters), y = 1.05, data = gender_ci3, colour = "darkorange")
###########

# income

income_glm <- svyglm(correct~income4-1, design=survey_123, family=quasibinomial(), subset = task=="cd")
income_ci <- broom::tidy(income_glm) %>%
  mutate(
    income4 = factor(levels(round_123$income4), levels = levels(round_123$income4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

income_glm3 <- svyglm(correct3~income4-1, design=survey_123, family=quasibinomial(), subset = task=="cd")

income_ci3 <- broom::tidy(income_glm3) %>%
  mutate(
    income4 = factor(levels(round_123$income4), levels = levels(round_123$income4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
income_compare <- glht(income_glm, mcp(income4="Tukey"))
income_compare3 <- glht(income_glm3, mcp(income4="Tukey"))

# get letters for each confidence
income_ci$letters <- cld(income_compare)$mcletters$Letters
income_ci3$letters <- cld(income_compare3)$mcletters$Letters

income_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = income4)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="right",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby income") +
   geom_segment(
  aes(
    x = as.numeric(income4) - 0.45,
    y = estimate,
    xend = as.numeric(income4) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = income_ci
) +
geom_segment(
  aes(
    x = as.numeric(income4) - 0.45,
    y = estimate,
    xend = as.numeric(income4) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = income_ci3
) +
geom_rect(
  aes(
    xmin = as.numeric(income4) - 0.45,
    ymin = low,
    xmax = as.numeric(income4) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = income_ci
) +
geom_rect(
  aes(
    xmin = as.numeric(income4) - 0.45,
    ymin = low,
    xmax = as.numeric(income4) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = income_ci3
) +
  scale_y_continuous("Percentage", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25), limit=c(-.05, 1.05))  +
 geom_text(aes(label=letters), y = -0.05, data = income_ci, colour = "steelblue") +
 geom_text(aes(label=letters), y = 1.05, data = income_ci3, colour = "darkorange")

income_glm <- svyglm(correct~income4-1, design=survey_123, family=quasibinomial(), subset = task=="ab")
income_ci <- broom::tidy(income_glm) %>%
  mutate(
    income4 = factor(levels(round_123$income4), levels = levels(round_123$income4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

income_glm3 <- svyglm(correct3~income4-1, design=survey_123, family=quasibinomial(), subset = task=="ab")

income_ci3 <- broom::tidy(income_glm3) %>%
  mutate(
    income4 = factor(levels(round_123$income4), levels = levels(round_123$income4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
income_compare <- glht(income_glm, mcp(income4="Tukey"))
income_compare3 <- glht(income_glm3, mcp(income4="Tukey"))

# get letters for each confidence
income_ci$letters <- cld(income_compare)$mcletters$Letters
income_ci3$letters <- cld(income_compare3)$mcletters$Letters

income_ab <- round_123_long %>% 
  filter(task=="ab") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = income4)) + 
  facet_grid(.~task) + 
  geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="right",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby income") +
   geom_segment(
  aes(
    x = as.numeric(income4) - 0.45,
    y = estimate,
    xend = as.numeric(income4) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = income_ci
) +
geom_segment(
  aes(
    x = as.numeric(income4) - 0.45,
    y = estimate,
    xend = as.numeric(income4) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = income_ci3
) +
geom_rect(
  aes(
    xmin = as.numeric(income4) - 0.45,
    ymin = low,
    xmax = as.numeric(income4) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = income_ci
) +
geom_rect(
  aes(
    xmin = as.numeric(income4) - 0.45,
    ymin = low,
    xmax = as.numeric(income4) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = income_ci3
) +
  scale_y_continuous("Percentage", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25), limit=c(-.05, 1.05))  +
 geom_text(aes(label=letters), y = -0.05, data = income_ci, colour = "steelblue") +
 geom_text(aes(label=letters), y = 1.05, data = income_ci3, colour = "darkorange")

age_glm <- svyglm(correct~age4-1, design=survey_123, family=quasibinomial(), subset = task=="cd")
age_ci <- broom::tidy(age_glm) %>%
  mutate(
    age4 = factor(levels(round_123$age4), levels = levels(round_123$age4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

age_glm3 <- svyglm(correct3~age4-1, design=survey_123, family=quasibinomial(), subset = task=="cd")

age_ci3 <- broom::tidy(age_glm3) %>%
  mutate(
    age4 = factor(levels(round_123$age4), levels = levels(round_123$age4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
age_compare <- glht(age_glm, mcp(age4="Tukey"))
age_compare3 <- glht(age_glm3, mcp(age4="Tukey"))

# get letters for each confidence
age_ci$letters <- cld(age_compare)$mcletters$Letters
age_ci3$letters <- cld(age_compare3)$mcletters$Letters

age_cd <- round_123_long %>% 
  filter(task=="cd") %>%
  mutate(
    response3 = c("Wrong", "They are the same", "Correct")[correct+correct3+1],
    response3 = factor(response3, levels=rev(c("Correct", "They are the same", "Wrong"))),
    task = factor(task, levels=c("cd", "ab"), labels=c("Aligned", "Unaligned")),
    chart = factor(chart, levels=c("Vertical", "Horizontal", "Horizontal wide"))
  ) %>% 
  ggplot(aes(x = age4)) + 
   facet_grid(.~task) + 
 geom_bar(aes(fill = response3, weight = weight), position="fill") +
  theme(legend.position="none",
        axis.text.x = element_text(angle=30, hjust=1)) + 
  scale_fill_manual("Response", values=c("orange", "grey", "steelblue")) +
  xlab("") +
    ggtitle("\nby age") +
   geom_segment(
  aes(
    x = as.numeric(age4) - 0.45,
    y = estimate,
    xend = as.numeric(age4) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = age_ci
) +
geom_segment(
  aes(
    x = as.numeric(age4) - 0.45,
    y = estimate,
    xend = as.numeric(age4) + 0.45,
    yend = estimate
  ),
  alpha = 1, colour = "black", linewidth = 0.25,
  data = age_ci3
) +
geom_rect(
  aes(
    xmin = as.numeric(age4) - 0.45,
    ymin = low,
    xmax = as.numeric(age4) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = age_ci
) +
geom_rect(
  aes(
    xmin = as.numeric(age4) - 0.45,
    ymin = low,
    xmax = as.numeric(age4) + 0.45,
    ymax = high,
  ),
  fill = "black", alpha = 0.25, #colour = "white", linewidth = 0.25,
  data = age_ci3
) +
  scale_y_continuous("Percentage", breaks=seq(0,1,by=0.25), labels = 100*seq(0,1,by=0.25), limit=c(-.05, 1.05))  +
 geom_text(aes(label=letters), y = -0.05, data = age_ci, colour = "steelblue") +
 geom_text(aes(label=letters), y = 1.05, data = age_ci3, colour = "darkorange")

age_glm <- svyglm(correct~age4-1, design=survey_123, family=quasibinomial(), subset = task=="ab")
age_ci <- broom::tidy(age_glm) %>%
  mutate(
    age4 = factor(levels(round_123$age4), levels = levels(round_123$age4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

age_glm3 <- svyglm(correct3~age4-1, design=survey_123, family=quasibinomial(), subset = task=="ab")

age_ci3 <- broom::tidy(age_glm3) %>%
  mutate(
    age4 = factor(levels(round_123$age4), levels = levels(round_123$age4)),
    low = estimate-1.96*std.error,
    high = estimate+1.96*std.error,
    estimate = inv_logit(estimate),
    low = inv_logit(low),
    high = inv_logit(high))

# create all pairwise comparisons for tasks and questions.
age_compare <- glht(age_glm, mcp(age4="Tukey"))
age_compare3 <- glht(age_glm3, mcp(age4="Tukey"))

# get letters for each confidence
age_ci$letters <- cld(age_compare)$mcletters$Letters
age_ci3$letters <- cld(age_compare3)$mcletters$Letters
